%%% LaTeX Template: Designer's CV
%%%
%%% Source: http://www.howtotex.com/
%%% Feel free to distribute this template, but please keep the referal to HowToTeX.com.
%%% Date: March 2012


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Document properties and packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper,12pt,final]{memoir}

% misc
\renewcommand{\familydefault}{bch}	% font
\pagestyle{empty}					% no pagenumbering
\setlength{\parindent}{0pt}			% no paragraph indentation


% required packages (add your own)
\usepackage{flowfram}										% column layout
\usepackage[top=1cm,left=1cm,right=1cm,bottom=1cm]{geometry}% margins
\usepackage{graphicx}										% figures
\usepackage{url}											% URLs
\usepackage[usenames,dvipsnames]{xcolor}					% color
\usepackage{multicol}										% columns env.
	\setlength{\multicolsep}{0pt}
\usepackage{paralist}										% compact lists
\usepackage{tikz}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Create column layout
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% define length commands
\setlength{\vcolumnsep}{\baselineskip}
\setlength{\columnsep}{\vcolumnsep}

% frame setup (flowfram package)
% left frame
\newflowframe{0.2\textwidth}{\textheight}{0pt}{0pt}[left]
	\newlength{\LeftMainSep}
	\setlength{\LeftMainSep}{0.2\textwidth}
	\addtolength{\LeftMainSep}{1\columnsep}
 
% small static frame for the vertical line
\newstaticframe{1.5pt}{\textheight}{\LeftMainSep}{0pt}
 
% content of the static frame
\begin{staticcontents}{1}
\hfill
\tikz{%
	\draw[loosely dotted,color=RoyalBlue,line width=1.5pt,yshift=0]
	(0,0) -- (0,\textheight);}%
\hfill\mbox{}
\end{staticcontents}
 
% right frame
\addtolength{\LeftMainSep}{1.5pt}
\addtolength{\LeftMainSep}{1\columnsep}
\newflowframe{0.7\textwidth}{\textheight}{\LeftMainSep}{0pt}[main01]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% define macros (for convience)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\Sep}{\vspace{1.5em}}
\newcommand{\SmallSep}{\vspace{0.5em}}

\newenvironment{AboutMe}
	{\ignorespaces\textbf{\color{RoyalBlue} About me}}
	{\Sep\ignorespacesafterend}
	
\newcommand{\CVSection}[1]
	{\Large\textbf{#1}\par
	\SmallSep\normalsize\normalfont}

\newcommand{\CVItem}[1]
	{\textbf{\color{RoyalBlue} #1}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Begin document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

% Left frame
%%%%%%%%%%%%%%%%%%%%


\begin{flushright}\small

	
	 \CVItem{\\ Contact} \\
	 
	\url{mahtab.farrokh@gmail.com}  \\
	(+98)9120764487 
	\CVItem{Address} \\
	424 Hafez Ave. \\
	Tehran\\
	Iran
	
\end{flushright}\normalsize
\framebreak


% Right frame
%%%%%%%%%%%%%%%%%%%%
\Huge\bfseries {\color{RoyalBlue} Mahtab Farrokh} \\
\Large\bfseries  Undergraduate Hardware Engineering \\

\normalsize\normalfont

% About me
%\begin{AboutMe}
%Lorem ipsum dolor sit amet, consectetur adipiscing elit. Vivamus vel %bibendum metus. Proin rutrum pharetra molestie. Cras sollicitudin %nulla nec leo lobortis in tristique purus pretium. Ut eu felis nulla. %Pellentesque condimentum justo ut ligula feugiat nec facilisis tellus %ultricies. Nullam sit amet dictum ipsum. Sed lacus neque, hendrerit eu %rhoncus nec, pellentesque vitae sem.
%\end{AboutMe}

\CVSection{Interests}
	\CVItem{Professional}
	\\
	Internet of Things, Android Programming, Graph theory
	\\
	\CVItem{Personal}
	\\
	Violin, Pottery, Wood Handcraft
	
\Sep

% Experience
\CVSection{Education}
\CVItem{2015 - 2019, B.Sc. in Computer Hardware Engineering}\\
AmirKabir University of Technology (Tehran Polytechnic), Tehran, Iran
GPA(up to now): 16.5
Total Passed Credits: 33
\SmallSep

\CVItem{2008 - 2015, Diploma in Physics and Mathematics Discipline}\\
Farzanegan 1,Tehran, Iran (NODET)
Attended Iran National Olympiad in Computer Focused on Combinatorics
, graph theory and c++ Programming.
GPA: 19.36/20
\Sep

\CVSection{Honors and Awards}
\begin{itemize}
	\item Ranked top 0.4 \% among more than 180,000 students participated
in the nationwide entrance examination of undergraduate studies
in Iranian universities (2015) 
	\item Semi-finalist at National Mathematics Olympiad (March 2013)
	\item accepted for 2nd level of Kharazmi awards assessments(2011)
	\item Member of National Organization for Development of Exceptional  Talents (NODET)(2007-2014)
 
\end{itemize}

\Sep



\CVSection{Teaching Experience}
	\begin{itemize}
	\item  Teacher Assistant, Introduction to Programming, Amirkabir University of technology, Under Supervision of Prof.Bakhshi (Fall-2016)
	\end{itemize}
\Sep

\newpage
\normalsize\normalfont
\framebreak
\framebreak
\\

\CVSection{Skills}
\CVItem{Programming}
\begin{multicols}{3}
\begin{compactitem}[\color{RoyalBlue}$\circ$]
	\item Python 3
	\item Java
	\item C and C++
	\item Verilog
	
\end{compactitem}
\end{multicols}
\SmallSep
\CVItem{Web and DB Technologies}
\begin{multicols}{3}
\begin{compactitem}[\color{RoyalBlue}$\circ$]
	\item MySQL 
	\item HTML(Familiar)
\end{compactitem}
\end{multicols}
\SmallSep
\CVItem{Operating Systems}
\begin{multicols}{3}
\begin{compactitem}[\color{RoyalBlue}$\circ$]
	\item Linux
	\item Windows
\end{compactitem}
\end{multicols}
\SmallSep
\CVItem{Typesetting}
\begin{multicols}{3}
\begin{compactitem}[\color{RoyalBlue}$\circ$]
	\item \LaTeX
	\item Vim
	\item Microsoft Word
\end{compactitem}
\end{multicols}
\SmallSep
\CVItem{Others}
\begin{multicols}{3}
\begin{compactitem}[\color{RoyalBlue}$\circ$]
	\item Qt
	\item Eclipse
	\item IntelliJ
	\item Pycharm
	\item Android Studio
\end{compactitem}
\end{multicols}

\Sep 

\CVSection{Projects}
\begin{itemize}
	\item Data Structure : search engine using inverted index algorithm - Python.
	
	\item Advanced Computer Programming:
		\begin{itemize}[$\circ$]
		\item  Implementation of a graphical game with multiplayer support and AI. Computer Player.(Strategic Game) - Java.
     	\item Implementation of Pacman game - Java.
	    \item Implementation of Arcade game - Java.
		\end{itemize}
		
	\item Principles of Computer and Programming : living cell simulation - C.
	\item Implementation of Notepad using Qt - C++.
	\item Wind Tonel for Educational purpose. Test room dimention 3000
$cm^{3}$.
	\item Hovercraft modeling for phisics workshop.Selected for 2nd level of Kharazmi awards assessment(2011)
 
\end{itemize}

\Sep

\CVSection{High Grades in undergraduate courses}
	\begin{itemize}
		\item  Advanced Computer Programming - Mr. Poorvatan - Spring 2016 - (18/20)
		\item Principles of Computer and Programming - Dr.Bakhshi - Fall 2015 -(20/20)
	\end{itemize}

\newpage
\normalsize\normalfont
\framebreak
\framebreak
\\

\CVSection{Extra-Curricular Activities}
	\begin{itemize}
		\item Member of Execution Committee, 8th National AUT Linux Festival - Spring 2016
		\item Member of Execution Committee, 2nd International AUT ACM ICPC - Fall 2016
	\end{itemize}
	
\CVSection{References}
	\begin{itemize}
		\item {Professor Bahador Bakhshi, Assistant Professor \\
Computer Engineering and IT Department, Amirkabir University of Technology\\
Email: bbakhshi@aut.ac.ir}
	\end{itemize}

\end{document}